Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2018-06-24 WholePlotTrajectories.tex
Update WholePlotTrajectories.tex

Both communities taxonomic and functional diversities and composition
proved resilient, following similar humped shaped trajectories returning
towards initial values. Communities functional structure is the most
direct link between biodiversity and ecosystem functioning
\citep{Diaz2005} and its resilience meant the recovery of ecosystem
processes in the long term \citep{Guariguata2001}. The resilience of
communities taxonomy in turn meant the maintenance of their initial
differences in species composition and diversity. The maintenance of
initial differences suggested the existence of multiple stable
equilibria as assumed for highly diverse and productive ecosystems
\citep{Chase2003} and the dependency of recovery trajectories on the
initial composition to be recovered
\citep{Hubbell1999, Molino2001, Anderson2007, Baraloto2012a}.

>>>>

Both communities taxonomic and functional diversities and composition
proved resilient, following similar humped-shaped trajectories starting to return
towards initial values 30 years after disturbance. Communities functional signature is the most
direct link between biodiversity and ecosystem functioning
\citep{Diaz2005} and its resilience meant the recovery of ecosystem
processes in the long term \citep{Guariguata2001}. The resilience of
communities taxonomy, despite the multiple NMDS starting points, suggest the long-term maintenance of the initial
differences in species composition and diversity, in turn suggesting the existence of multiple stable
equilibria as assumed for highly diverse and productive ecosystems
\citep{Chase2003} and the dependency of recovery trajectories on the
initial composition to be recovered
\citep{Hubbell1999, Molino2001, Anderson2007, Baraloto2012a}.
